Most of the attributes have self explanatory name.
Possibly, the only exception is {\it Period} dimension in {\it Subscription} fact. The {\it Period} describes different types of subscriptions based on how long the subscription last. 

We managed to get all data which fit our hierarchies completely, so we do not have any optional attributes nor we use any convergences. 

\subsection*{Article popularity attributes} 
The biggest hierarchy is in {\it Article title}, which has attached hierarchies of {\it Subcategory}, {\it Category} and the hierarchy {\it Day}, {\it Month}, {\it Year} together with {\it Author} hierarchy. The {\it Date} hierarchy in {\it Article} dimension represents publication date.

We decided to completely separate dimension {\it Day of week} from {\it Time} dimension, because we have no interest in rolling up using {\it Day of week}.

\subsection*{Subscription attributes}
In this fact we also separated {\it Day of a week} and we also used hierarchies {\it Date}. However, we added {\it Week} and different {\it "Holidays"} in the hierarchy after the {\it Day}. We did not separate it completely, because we are interested which day of month is the most important, so we can aggregate over a day.

Another thing worth to note is that {\it Order} is a descriptive attribute of {\it Period}, so we can not aggregate over it.

\subsection*{Advertisement attributes} 
This is out simplest fact and contains only hierarchy of {\it Date} and hierarchy of {\it Campaign}.
The {\it Campaign} hierarchy contains {\it Advertiser category}, which describes how important The Journal managers that the advertiser is. The {\it Advertiser category} allows us to find out how well we rate our customers in time.
