This chapter contains report from the $1^{st}$  Milestone which purpose was to design a data warehouse from chosen domain. We divided the tasks into several sections, which we now introduce.

The Section~\ref{sec:ml1_domain} describes business domain of a company which we have chosen for our sample data warehouse. The Subsections~\ref{sub:ml1_objectives},~\ref{sub:ml1_processes},~\ref{sub:ml1_granularity} will introduce  step by step the~data warehouse objectives, the~business processes and finally the granularity of the processes. The objectives will tell you why we need the data warehouse. The~business processes will present you the core of the organisation and last but not least the granularity of the~processes show you how detail view we want to capture.

The next Section~\ref{sec:ml1_design} we concentrate on the conceptual modeling. In Subsections~\ref{sub:ml1_facts} we define our facts and in Subsections~\ref{sub:ml1_measures},~\ref{sub:ml1_attributes} the measures, attributes and their hierarchies are depicted. In these sections the aggregation of measures is introduced and we remind the process granularity which we apply on our facts.

In~the Section~\ref{sec:ml1_logical} we will depict two alternatives in logical design. Concretaly, in Subsection~\ref{sub:ml1_star} is presented star schema of our facts and in Subsection~\ref{sub:ml1_snowflake} we show snowflake schema. At the end, in~Subsection~\ref{sub:ml1_choice} we argue why we have chosen the star schema. 

The~final Section~\ref{sec:implementation} describes the data and the scripts we used to populate our database. 
